The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The \astropy project supports and fosters the development of open-source
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the \astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the \astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate and support
development for a broader ecosystem of inter-operable packages.
We conclude with a future outlook of planned new features and directions for the
broader \astropy project.
\end{abstract}

@@

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
Central to the success of \astropy is an open environment where
anybody can contribute to the code by opening a so-called ``pull
request'' with a new code contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}; this
request is then reviewed by a maintainer responsible for the specific
sub-package and possibly merged into the main code base. Most bug
fixes and small features are contributed in this way. However, this
model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces. Thus, \astropy has a mechanism to more formally propose
changes to the code management (e.g.~the release cycle) or to plan
out major new features. This mechanism is called ``Astropy Proposal
for Enhancement'' (APE). In an APE one or more authors lay out a
vision for a new feature, including a rationale why this feature is
needed, how it should be implemented, and what the interface will
be. These APEs are discussed and refined before much work is invested
into a detailed implementation. APEs are again edited and discussed on
a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
open to the public. In previous APEs a community consensus emerged and
APEs are accepted and become the basis for future work at this
point. In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in
question. APEs are modeled after the ``Python Enhancement Proposals''
(PEP) and guide the development of the \python programming language.

@@

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python package that is not part of the \astropypkg core package, but
has requested to be included as part of the astropy project’s
community. These packages support the goals and vision of \astropy of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation. \astropypkg
version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
are strongly encouraged to support at least \python~3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. In general we hope that
becoming an affiliated package is seen as a good way for new and existing
packages to gain exposure.
%
% TODO: write about the process of becoming affiliated, and project packages
%
\subsection{Mixin}

@@

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment

\subsection{Units and quantities}
\label{sec:units}
% Marten, Adrian

>>>>

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The \astropy project supports and fosters the development of open-source and open-development
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the \astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the \astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate and support
development for a broader ecosystem of inter-operable packages.
We conclude with a future outlook of planned new features and directions for the
broader \astropy project.
\end{abstract}

@@

\subsection{APEs - Astropy Proposals for Enhancement}
%draft by hamogu
Central to the success of \astropy is an open environment where
anybody can contribute to the code by opening a so-called ``pull
request'' with a new code contribution on a publically available
website\footnote{\url{https://github.com/astropy/astropy}}; this
request is then reviewed by at least one of the maintainers responsible for the specific
sub-package and possibly merged into the main code base. Most bug
fixes and small features are contributed in this way. However, this
model leads to ``organic'' growth where different features are
implemented by different people with different programming styles and
interfaces. Thus, \astropy has a mechanism to more formally propose
changes to the code management (e.g.~the release cycle) or to plan
out major new features. This mechanism is called ``Astropy Proposal
for Enhancement'' (APE). In an APE one or more authors lay out a
vision for a new feature, including a rationale why this feature is
needed, how it should be implemented, and what the interface will
be. These APEs are discussed and refined before much work is invested
into a detailed implementation. APEs are again edited and discussed on
a platform \footnote{\url{https://github.com/astropy/astropy-APEs}}
open to the public. In previous APEs a community consensus emerged and
APEs are accepted and become the basis for future work at this
point. In cases where consensus cannot be reached, the
\astropy coordination committee can decide to close the discussion and
make an executive decision based on the community input on the APE in
question. APEs are modeled after the ``Python Enhancement Proposals''
(PEP) and guide the development of the \python programming language.

@@

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up
%
\par A major part of the \astropy~project is the concept of
``Affiliated Packages''. An affiliated package is an astronomy-related
\python~package that is not part of the \astropypkg~core package, but
has requested to be included as part of the \astropy project's
community. These packages support the goals and vision of \astropy~of
improving code reuse, interoperability, and embracing good coding
practices such as testing and thorough documentation. \astropypkg{}
version 2.0 supports \python~2.7 and \python~3.4+, affiliated packages
are strongly encouraged to support at least \python~3.x.
%
\par Affiliated packages contain functionality that is more specialized, or
have license incompatibility, or have enough external dependencies (e.g. GUI
libraries) that limit their integration possibility into the core and thus
they are more suitable to be separate packages. Starting as an affiliate 
package is also seen as a good strategy for functionality that is aimed for
the \astropypkg~core but is currently undergo rapid development and can 
benefit from a different release cycle while stabilizing its API. 
%
\par In general we hope that becoming an affiliated package is seen as 
a good way for new and existing packages to gain exposure.
%
\inlinecomment{BMS}{TODO: write about the process of becoming affiliated, and project packages}
%
\subsection{Mixin}

@@

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
\subsection{Units and quantities}
\label{sec:units}
% Marten, Adrian
